Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
width of fig should be ~8cm, not \columnwidth
add missing ref to Venkitaraman2014

Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment \cite{Venkitaraman2014} \ml{missing ref}, as shown in Figure \ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelope of Gammatone wavelets is more biologically plausible than the symmetric, Gaussian-like envelope of the widespread Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking \cite{Fastl2007}.
Moreover, it should be noted that Gammatone wavelets follow the typical amplitude profile of natural sounds, beginning with a relatively sharp attack and ending with a slower decay.
As such, they can be discovered by unsupervised encoding of natural sounds \cite{Smith2006}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test3.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with logarithmic compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without logarithmic compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}

>>>>

Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment \cite{Venkitaraman2014}, as shown in Figure \ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelope of Gammatone wavelets is more biologically plausible than the symmetric, Gaussian-like envelope of the widespread Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking \cite{Fastl2007}.
Moreover, it should be noted that Gammatone wavelets follow the typical amplitude profile of natural sounds, beginning with a relatively sharp attack and ending with a slower decay.
As such, they can be discovered by unsupervised encoding of natural sounds \cite{Smith2006}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test3.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with logarithmic compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without logarithmic compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}
